### 2014-10-30 intro.tex
intro

\begin{itemize}
\setlength{\itemsep}{2pt}
\item We introduce \name, a Haskell library that supports the description
  and validation of replicated data types found in programs intended to
  execute on eventually consistent stores. Contracts are used to specify
  fine-grained application-level consistency properties, and are analyzed to
  assign the most efficient and sound store consistency level to the
  corresponding operation.
\item \name supports coordination-free transactions over arbitrary datatypes.
	We extend our contract language to express fine-grained transaction isolation
	guarantees, and utilize the contract enforcement system to automatically
	assign the correct and most efficient isolation level for a transaction.
\item We provide metatheory that certifies the soundness of our contract
	enforcement system, and ensures that an operation is only executed if the
	required conditions on consistency are met.
\item An implementation of \name as a transparent shim layer over
	Cassandra~\cite{Cassandra}, a well-known general-purpose data store.  An
	extensive experimental evaluation over a collection of real-world
	applications, including a Twitter-like micro-blogging site and an eBay-like
	auction site illustrates the practicality of our approach.
\end{itemize}

>>>>

\begin{itemize}
\setlength{\itemsep}{2pt}
\item We introduce \name, a shallow extension of Haskell that supports the description
  and validation of replicated data types found in programs intended to
  execute on eventually consistent stores. Contracts are used to specify
  fine-grained application-level consistency properties, and are analyzed to
  assign the most efficient and sound store consistency level to the
  corresponding operation.
\item \name supports coordination-free transactions over arbitrary datatypes.
	We extend our contract language to express fine-grained transaction isolation
	guarantees, and utilize the contract enforcement system to automatically
	assign the correct and most efficient isolation level for a transaction.
\item We provide metatheory that certifies the soundness of our contract
	enforcement system, and ensures that an operation is only executed if the
	required conditions on consistency are met.
\item An implementation of \name as a transparent shim layer over
	Cassandra~\cite{Cassandra}, a well-known general-purpose data store.  An
	extensive experimental evaluation over a collection of real-world
	applications, including a Twitter-like micro-blogging site and an eBay-like
	auction site illustrates the practicality of our approach.
\end{itemize}
